hbm_paper_results

### 2024-01-10 paper_prop_results.Rmd
working through ratio results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")

source("./cubic_scripts/R_scripts/gamlss_helper_funs.R")
source("./cubic_scripts/R_scripts/ranked_welch_tests.R")
aseg_cerebrum <- readRDS(file="/Users/megardn/Desktop/BGD_Repos/ggseg_atlas/aseg_cerebrum_atlas.RDS")
```

single script to parse outputs & get results (condensed from `ukb_sim.site_analyses.Rmd`)

@@

```{r}
ratio_data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/ukb_ratio"
raw_files <- list.files(path = ratio_data_path, pattern = "_diffs.csv", full.names = TRUE)

@@

# #sum(is.na(ratio.df))
# na.df <- ratio.df[rowSums(is.na(ratio.df)) > 0,]
# skimr::skim(na.df)
# 
# names(ratio.df)
ratio.df[is.na(ratio.df$diff_lh_CT_cuneus.z),] %>%
  dplyr::select(contains("_cuneus"), "participant", "dataset")
```

@@

```{r}
raw_files <- list.files(path = ratio_data_path, pattern = "_subj_pred.csv", full.names = TRUE)

@@

```{r}
for (l in unique(ratio_subj.df$dataset)){
plot <- ratio_subj.df %>%
  dplyr::filter(dataset == l) %>%
  ggplot(aes(x=mean_centile, y=mean_cent_diff, color=sex)) +
  geom_point(alpha=0.3) +
  geom_smooth() +
  facet_grid(sim.site ~ prop) +
  ggtitle(l)
print(plot)
}
```

Do centile scores change based on combat version?

need to look and see what happens for subjects who aren't in all samples?

@@

```{r, eval=FALSE}
#too much memory to run!
ratio.df %>%
  dplyr::select(sim.site, prop, dataset, starts_with("abs.diff"), !ends_with(".z")) %>%
  pivot_longer(cols= starts_with("abs.diff"), names_to="pheno", nammes_prefix="abs.diff_", values_to="cent_abs.diff") %>%
  mutate(cent_abs.diff = cent_abs.diff * 100) %>%
  ggplot() +
    geom_boxplot(aes(x=prop, y=cent_abs.diff, fill=dataset)) +
  labs(y= "Magnitude Centile Error", x = "M:F Ratio in Site B") +
  ggtitle("Error in centile scores across ComBat \nconfigurations as sex imbalance changes")
```

Plot w/in subj means

```{r}
ratio_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff * 100) %>%
  ggplot() +
    geom_boxplot(aes(x=prop, y=mean_cent_abs.diff, fill=dataset)) +
  labs(y= "Magnitude Centile Error", x = "M:F Ratio in Site B") +
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat \nconfigurations as sex imbalance changes")

ratio_subj.df %>%
  ggplot() +
    geom_boxplot(aes(x=prop, y=mean_z_abs.diff, fill=dataset)) +
  labs(y= "Magnitude Z-score Error", x = "M:F Ratio in Site B") +
  ggtitle("Within-subject mean magnitude of error in z-scores across ComBat \nconfigurations as sex imbalance changes")
```

W/in subj average plots

```{r}
cent.diffs.v.plot.r <- ratio_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=mean_cent_abs.diff, fill=dataset), scale="width") +
  labs(y= "Magnitude Centile Error", x = "ComBat Configurations") +
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat \nconfigurations while varying M:F")
cent.diffs.v.plot.r
ggsave(filename="figs/ratio_centile_violin.png", cent.diffs.v.plot.r)
```

@@

```{r}
prop_abs.cent_t.tests <- mclapply(ratio_list, centile.t.tests, comp_multiplier=11, mc.preschedule = FALSE) #FDR correction across 11 M:F permutations
names(prop_abs.cent_t.tests) <- n_prop_list
prop_abs.cent_t.tests_df <- bind_rows(prop_abs.cent_t.tests, .id = "column_label")
```

Visalize
```{r}
ggplot(prop_abs.cent_t.tests_df) +
  geom_col(aes(x=column_label, y=n_sig_regions, fill=column_label)) +
  geom_hline(yintercept = 208, linetype='longdash') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position="none") +
  facet_wrap(~comp)
```

## Sex-Biases

```{r}
ratio_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=mean_cent_abs.diff, fill=sex), scale="width") +
  facet_wrap(~dataset) +
  labs(y= "Magnitude Centile Error", x = "ComBat Configurations") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat \nconfigurations while varying M:F")
```

```{r}
cent.diffs.v.boxplot.r_sex_free <- ratio_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_boxplot(aes(x=prop, y=mean_cent_abs.diff, fill=sex)) +
  facet_wrap(~dataset, scale="free_y") +
  labs(y= "Magnitude Centile Error", x = "ComBat Configurations") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat \nconfigurations while varying M:F")
cent.diffs.v.boxplot.r_sex_free
ggsave(filename="figs/ratio_centile_box_sex_free.png", cent.diffs.v.boxplot.r_sex_free)
```

```{r}
#trying to add significance testing
abs.cent.diffs.by.sex.stat.test <- ratio_subj.df %>%
  dplyr::filter(dataset != "cf") %>% #because it's the same as cf.lm
  group_by(dataset, prop) %>%
  wilcox_test(mean_cent_abs.diff ~ sex) %>%
  adjust_pvalue(method = "fdr") %>%
  add_significance() %>%
  add_xy_position(x = "prop")

abs.cent.diffs.v.boxplot.r_sex <- ratio_subj.df %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  dplyr::filter(dataset != "cf") %>% #because it's the same as cf.lm
  droplevels() %>%
  ggplot() +
  geom_boxplot(aes(x=prop, y=mean_cent_abs.diff, fill=sex)) +
  facet_wrap(~dataset) +
  labs(y= "Mean Magnitude Centile Error", x = "Site B M:F") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  stat_pvalue_manual(
    cent.diffs.by.sex.stat.test, label = "p.adj.signif", tip.length = 0, bracket.shorten=0.005,
    #hide.ns = TRUE
    bracket.nudge.y = -0.5
    ) +
  ggtitle("Within-subject error in centile scores across ComBat configurations while varying M:F")
cent.diffs.v.boxplot.r_sex
ggsave(filename="figs/ratio_abs.centile_box_sex.png", abs.cent.diffs.v.boxplot.r_sex, width = 25, height = 12, units = "cm")
```

eval diffs (not abs. diffs)

```{r}
#trying to add significance testing
cent.diffs.by.sex.stat.test <- ratio_subj.df %>%
  dplyr::filter(dataset != "cf") %>% #because it's the same as cf.lm
  group_by(dataset, prop) %>%
  wilcox_test(mean_cent_diff ~ sex) %>%
  adjust_pvalue(method = "fdr") %>%
  add_significance() %>%
  add_xy_position(x = "prop")

cent.diffs.v.boxplot.r_sex <- ratio_subj.df %>%
  mutate(mean_cent_diff = mean_cent_diff*100) %>% #for visuals
  dplyr::filter(dataset != "cf") %>% #because it's the same as cf.lm
  droplevels() %>%
  ggplot() +
  geom_boxplot(aes(x=prop, y=mean_cent_diff, fill=sex)) +
  facet_wrap(~dataset) +
  labs(y= "Mean Magnitude Centile Error", x = "Site B M:F") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  stat_pvalue_manual(
    cent.diffs.by.sex.stat.test, label = "p.adj.signif", tip.length = 0, bracket.shorten=0.005,
    #hide.ns = TRUE
    bracket.nudge.y = 4.5
    ) +
  ggtitle("Within-subject error in centile scores across ComBat configurations while varying M:F")
cent.diffs.v.boxplot.r_sex
ggsave(filename="figs/ratio_centile_box_sex.png", cent.diffs.v.boxplot.r_sex, width = 25, height = 12, units = "cm")
```

### Significance Testing

#### CENTILES
within each M:F prop, test male vs female subject's mean abs. centile diff
```{r}
sex_bias_ratio_abs.tests <- mclapply(ratio_subj_list, sex.bias.t.tests, mc.preschedule = FALSE, comp_multiplier = 11)
names(sex_bias_ratio_abs.tests) <- n_prop_list
sex_bias_ratio_abs.tests_df <- bind_rows(sex_bias_ratio_abs.tests, .id = "prop")
```

Visualize
```{r}
sex_bias_ratio_abs.tests_df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  mutate(dataset = factor(dataset, levels = c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         prop = factor(prop, levels=n_prop_list, ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=prop, fill=sex_diff)) + 
    geom_raster() +
    paletteer::scale_fill_paletteer_c("ggthemes::Classic Green-Blue") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    coord_fixed()
```

test actual (not abs. val) centile errors

```{r}
sex_bias_ratio_tests <- mclapply(ratio_subj_list, sex.bias.t.tests, to_test = "mean_cent_diff", mc.preschedule = FALSE, comp_multiplier = 11)
names(sex_bias_ratio_tests) <- n_prop_list
sex_bias_ratio_tests_df <- bind_rows(sex_bias_ratio_tests, .id = "prop")
```

Visualize
```{r}
sex_bias_ratio_tests_df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  mutate(dataset = factor(dataset, levels = c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         prop = factor(prop, levels=n_prop_list, ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=prop, fill=sex_diff)) + 
    geom_raster() +
    paletteer::scale_fill_paletteer_c("ggthemes::Classic Green-Blue") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    coord_fixed()
```

#### Z-SCORES

```{r}
sex_bias_ratio_abs.tests.z <- mclapply(ratio_subj_list, sex.bias.t.tests, to_test ="mean_z_abs.diff", mc.preschedule = FALSE, comp_multiplier = 11)
names(sex_bias_ratio_abs.tests.z) <- n_prop_list
sex_bias_ratio_abs.tests.z_df <- bind_rows(sex_bias_ratio_abs.tests.z, .id = "prop")
```

Visualize
```{r}
sex_bias_ratio_abs.tests.z_df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  mutate(dataset = factor(dataset, levels = c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         prop = factor(prop, levels=n_prop_list, ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=prop, fill=sex_diff)) + 
    geom_raster() +
    paletteer::scale_fill_paletteer_c("ggthemes::Classic Green-Blue") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    coord_fixed()
```

```{r}
sex_bias_ratio_tests.z <- mclapply(ratio_subj_list, sex.bias.t.tests, to_test ="mean_z_diff", mc.preschedule = FALSE, comp_multiplier = 11)
names(sex_bias_ratio_tests.z) <- n_prop_list
sex_bias_ratio_tests.z_df <- bind_rows(sex_bias_ratio_tests.z, .id = "prop")
```

Visualize
```{r}
sex_bias_ratio_tests.z_df %>%
  dplyr::filter(sig_fdr == TRUE) %>%
  mutate(dataset = factor(dataset, levels = c("cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         prop = factor(prop, levels=n_prop_list, ordered=TRUE)) %>%
  ggplot(aes(x=dataset, y=prop, fill=sex_diff)) + 
    geom_raster() +
    paletteer::scale_fill_paletteer_c("ggthemes::Classic Green-Blue") +
    theme_classic() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    coord_fixed()
```

## Extremeness-Biases
Does a person's centile error depend on their true centile value (e.g., very low or very high centiles more or less likely to have errors)

#### CENTILES

test w/in subj avg centile ~ w/in subj avg centile error

```{r}
#testing
test.lm <- lm(mean_cent_diff ~ mean_centile*as.factor(dataset), data=ratio_subj_list[[1]])
tidy(test.lm)
interactions::interact_plot(test.lm, pred = mean_centile, modx = dataset)

ggplot(ratio_subj_list[[4]], aes(x=mean_centile, y=mean_cent_diff, color=sex)) +
  geom_point(alpha=0.3) +
  geom_smooth() +
  facet_wrap(~dataset, scales="free_y")
```

```{r}
ext.bias_test.ln <- mclapply(ratio_subj_list, extremeness.lm, f="mean_centile ~ mean_cent_diff", comp_multiplier= 33, mc.preschedule=FALSE)
names(ext.bias_test.ln) <- n_prop_list
linear <- as.data.frame(bind_rows(ext.bias_test.ln, .id = "prop"))

ext.bias_test.sq <- mclapply(ratio_subj_list, extremeness.lm, f="mean_centile ~ poly(mean_cent_diff, 2)", comp_multiplier= 33, mc.preschedule=FALSE)
names(ext.bias_test.sq) <- n_prop_list
square <- as.data.frame(bind_rows(ext.bias_test.sq, .id = "prop"))

ext.bias_test.cb <- mclapply(ratio_subj_list, extremeness.lm, f="mean_centile ~ poly(mean_cent_diff, 3)", comp_multiplier= 33, mc.preschedule=FALSE)
names(ext.bias_test.cb) <- n_prop_list
cubic <- as.data.frame(bind_rows(ext.bias_test.cb, .id = "prop"))

#one big dataframe
ext.bias_test.df <- bind_rows(linear, square, cubic, .id = "model")
```

summarize across modeling options

```{r}
ext.bias_test.df %>%
  group_by(dataset, prop) %>%
  dplyr::arrange(p.val_fdr) %>%
  slice(1) %>% #get lowest p-val
  ungroup()
```

#### Z-SCORES
```{r}
ext.bias_test.z.ln <- mclapply(ratio_subj_list, extremeness.lm, f="mean_z ~ mean_z_diff", comp_multiplier=33, mc.preschedule=FALSE)
names(ext.bias_test.z.ln) <- n_prop_list
linear <- as.data.frame(bind_rows(ext.bias_test.z.ln, .id = "prop"))

ext.bias_test.z.sq <- mclapply(ratio_subj_list, extremeness.lm, f="mean_z ~ poly(mean_z_diff, 2)", comp_multiplier= 33, mc.preschedule=FALSE)
names(ext.bias_test.z.sq) <- n_prop_list
square <- as.data.frame(bind_rows(ext.bias_test.z.sq, .id = "prop"))

extremeness.lm(ratio_subj_list[[2]], f="mean_z ~ poly(mean_z_diff, 2)")

ext.bias_test.z.cb <- mclapply(ratio_subj_list, extremeness.lm, f="mean_z ~ poly(mean_z_diff, 3)", comp_multiplier= 33, mc.preschedule=FALSE)
names(ext.bias_test.z.cb) <- n_prop_list
cubic <- as.data.frame(bind_rows(ext.bias_test.z.cb, .id = "prop"))

#one big dataframe
ext.bias_test.z.df <- bind_rows(linear, square, cubic, .id = "model")
```

summarize across modeling options

```{r}
ext.bias_test.z.df %>%
  group_by(dataset, prop) %>%
  dplyr::arrange(p.val_fdr) %>%
  slice(1) %>% #get lowest p-val
  ungroup()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain, ggh4x)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")

source("./cubic_scripts/R_scripts/stats_tests.R")
aseg_cerebrum <- readRDS(file="/Users/megardn/Desktop/BGD_Repos/ggseg_atlas/aseg_cerebrum_atlas.RDS")
```

@@

```{r}
raw_files <- list.files(path = paste0(data_path, "/ukb_ratio"), pattern = "_diffs.csv", full.names = TRUE)

@@

# #sum(is.na(ratio.df))
# na.df <- ratio.df[rowSums(is.na(ratio.df)) > 0,]
# skimr::skim(na.df)
# 
# names(ratio.df)
```

@@

```{r}
raw_files <- list.files(path = paste0(data_path, "/ukb_ratio"), pattern = "_subj_pred.csv", full.names = TRUE)

@@

Read in predicted centiles & z scores
```{r}
pred.csvs <- list.files(path = paste0(data_path, "/ukb_ratio"), pattern = "_predictions.csv", full.names = TRUE)
combined_preds <- data.frame()

df_list <- list() #new empty list
for (file in pred.csvs) {
  # Read each CSV file
  data <- fread(file)

  # Add a "Source_File" column with the file name
  data <- data %>%
    mutate(Source_File = as.factor(basename(file))) %>%
    mutate(dataset = gsub("_data|_data_predictions.csv|prop-|[0-9]|-", "", Source_File))

    # Bind the data to the combined dataframe
    df_list <- c(df_list, list(data))
    assign("ratio_pred_list", df_list)
}
dim(ratio_pred_list)

#merge into single df
ratio_pred.df <- bind_rows(ratio_pred_list)
```

Visualize sex-distribution across sites/proportions

```{r}
ratio.df %>%
  dplyr::filter(dataset=="cf") %>%
ggplot() +
  geom_bar(aes(x=prop, fill=sex)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~ sim.site)
```

## CENTILES

Do centile score errors change based on combat version?
*need to look and see what happens for subjects who aren't in all samples?*

@@

@@

```{r}
prop_abs.cent_t.tests <- mclapply(ratio_list, centile.t.tests, feature_list=pheno_abs.diff.list, comp_multiplier=11, mc.preschedule = FALSE) #FDR correction across 11 M:F permutations
names(prop_abs.cent_t.tests) <- n_prop_list
prop_abs.cent_t.tests_df <- bind_rows(prop_abs.cent_t.tests, .id = "column_label")
```

Visualize 
```{r}
ggplot(prop_abs.cent_t.tests_df) +
  geom_col(aes(x=column_label, y=n_sig_regions, fill=column_label)) +
  geom_hline(yintercept = 208, linetype='longdash') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position="none") +
  facet_wrap(~comp)
```

Plot errors for global phenotypes
```{r}
percent_f <- setNames(paste0(seq(from=100, to=0, by=-10), "% F"), unique(ratio_subj.df$prop))

prop.global_abs.diffs <- ratio.df %>%
  dplyr::select(participant, sex, age_days, sim.site, prop, dataset, paste0("abs.diff_", vol_list_global)) %>%
  pivot_longer(cols=starts_with("abs.diff_"), names_to="pheno", names_prefix="abs.diff_", values_to = "abs.diff")

prop.global_cent_errs_plot <- prop.global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE),
         abs.diff = abs.diff*100) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Magnitude Centile Error", x = "% Females in Imbalanced Study Site") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_x_discrete(labels=percent_f) +
  facet_wrap(~ pheno) +
  ggtitle("Magnitude errors in centile scores of global features across ComBat pipelines")
prop.global_cent_errs_plot
#ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

### Sex-Biases

Test subj. mean averages
```{r}
prop.sex.bias.test <- mclapply(ratio_subj_list, sex.bias.t.tests, mc.preschedule = FALSE, to_test = "mean_cent_abs.diff", comp_multiplier=11)
names(prop.sex.bias.test) <- n_prop_list
sex_bias_ratio_tests_df <- bind_rows(prop.sex.bias.test, .id = "prop")
```

```{r}
for (l in unique(ratio_subj.df$dataset)){
plot <- ratio_subj.df %>%
  dplyr::filter(dataset == l) %>%
  ggplot(aes(x=mean_centile, y=mean_cent_diff, color=sex)) +
  geom_point(alpha=0.3) +
  geom_smooth(method="lm") +
  facet_grid(sim.site ~ prop) +
  ggtitle(l)
print(plot)
}
```

```{r}
ratio_subj.df %>%
  dplyr::filter(dataset == "cf.lm" |dataset == "cf.gam" | dataset=="cf.gamlss") %>%
  ggplot(aes(x=mean_centile*100, y=mean_cent_diff*100, color=sex)) +
  geom_point(alpha=0.2) +
  #geom_smooth(method="lm") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_nested(dataset + sim.site ~ prop)

ratio_subj.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset=="cf.gamlss") %>%
  ggplot(aes(x=sim.site, y=mean_cent_diff*100)) +
  geom_violin() +
  #geom_smooth(method="lm") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_nested(dataset ~ prop)
```

```{r}
dataset_names <- c('ukb-CN-simsites' = "Raw Data", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")

prop_sex_mean_cent.plot <- ratio_subj.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset=="cf.gamlss") %>%
  ggplot(aes(x=sim.site, y=mean_cent_diff*100, fill=sex)) +
  geom_violin() +
  #geom_smooth(method="lm") +
  theme_linedraw(base_size=12) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(dataset ~ prop, labeller = labeller(dataset = as_labeller(dataset_names), prop=as_labeller(percent_f))) +
  xlab("Site") + ylab("Mean Centile Error")
prop_sex_mean_cent.plot
```

```{r}
dataset_names <- c('ukb-CN-simsites' = "Raw Data", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
percent_f <- setNames(paste0(seq(from=100, to=0, by=-10), "% F"), unique(ratio_subj.df$prop))

prop_sex_mean_cent.plot2 <- ratio_subj.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset=="cf.gamlss") %>%
  ggplot(aes(x=sex, y=mean_cent_diff*100, fill=sex)) +
  geom_violin() +
  #geom_smooth(method="lm") +
  theme_linedraw(base_size=12) +
  theme(axis.text.x = element_blank()) +
  facet_grid(dataset ~ prop, labeller = labeller(dataset = as_labeller(dataset_names), prop=as_labeller(percent_f))) +
  xlab("Site") + ylab("Mean Centile Error")
prop_sex_mean_cent.plot2
```

```{r}
prop_sex_mean_cent.plot.abs <- ratio_subj.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset=="cf.gamlss") %>%
  ggplot(aes(x=sex, y=mean_cent_abs.diff*100, fill=sex)) +
  geom_violin() +
  #geom_smooth(method="lm") +
  theme_linedraw(base_size=12) +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank(), legend.position="bottom") +
  facet_grid(dataset ~ prop, labeller = labeller(dataset = as_labeller(dataset_names), prop=as_labeller(percent_f))) +
  ylab("Mean Absolute Centile Error")
prop_sex_mean_cent.plot.abs
saveRDS(prop_sex_mean_cent.plot.abs, file="figs/mean_subj_cent_err.RDS")
```

*need to add w/in feature sex-bias testing, having issues with cubic*

### W/o extremes
Are extreme centiles (<5% and >95%) driving observed results?

Get raw centiles and merge with centile differences

```{r, warning=FALSE}
raw_centiles <- combined_preds %>%
  dplyr::filter(dataset == "ukb_CN")

merge.df <- full_join(raw_centiles, diffs.df)
unique(merge.df$dataset)
dim(raw_centiles)
dim(merge.df)

merge.df <- merge.df %>%
  dplyr::select(!File_ID)
```
